---
title: "Asymmetric alignment paper, data preprocessing script"
author: "Kenny Smith"
date: "23/1/2019"
output: html_document
---

The data produced by the experimental code is in a slightly awkward format (one line in training and recall tests includes data from a *pair* of trials, one produced by both participants. To facilitate analysis, we convert this to a format more ameanable to plotting etc.


```{r, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(plyr)
data.directory = 'RawData/'
source("RCode/findClosestMatch.R")
```


# Utility functions: Identify word order 

```{r}
#remove trailing/leading whitespace
trim <- function (x) gsub("^\\s+|\\s+$", "", x)

verbs <- c("wooshla","boingla")
nouns <- c("beeko", "trunko", "hoppo", "bugo", "oinko","fino")
particles <- c("bup", "dak", "jeb", "kem", "pag", "tid", "wib", "yav")
all.legal.words <- c(verbs,nouns,particles)

#this function takes a label and identifies the word order, using the findClosestMatch and the dictionaries defined above
identify.word.order <- function(label) {
  if (is.na(label)) {
    NA}  
  else 
  {words <- strsplit(label, ' ')[[1]] #split the label around spaces
   order <- ""
   for (w in words) {
     closest_legal_w <- findClosestMatch(trim(w),all.legal.words)
     if (is.element(closest_legal_w,verbs)){
       order <- paste(order,"V",sep="")}
     else if (is.element(closest_legal_w,nouns)) {
       order <- paste(order,"N",sep="")}
     else if (is.element(closest_legal_w,particles)){
       order <- paste(order,"P",sep="")}
     else {
       print("Error - no legal closest match?")
       order <- paste(order,"O",sep="")}
   }
   order
  }
}

#this assigns NA to illegal labels, i.e. that aren't VN or VNP, after individual-word correction
is.number.marked <- function(word.order) {
  if (is.na(word.order)) {
    NA
  }
  else if (word.order == "VNP") {
    TRUE}
  else if (word.order == "VN") {
    FALSE}
  else {NA}
}
```





# Import data and collate

```{r}

condition.66.33.pairs <- c(60,67,68,73,75,77,80,88,90,101,171,172,173,174,176,177,178,179,180,188)

condition.83.17.pairs <- c(61,64,66,69,70,72,78,82,94,98,102,181,182,183,184,185,186,187,189,190)

condition.100.66.pairs <- c(62,71,74,79,81,85,86,95,96,99,151,152,153,154,155,156,157,158,159,160)

condition.100.33.pairs <- c(63,65,76,83,84,89,91,92,93,97,100,161,162,163,164,165,166,167,168,169,170)

all.pairs <- c(condition.66.33.pairs,condition.83.17.pairs,
               condition.100.66.pairs,condition.100.33.pairs)

#utility function to look up pair and label condition
pair.to.condition <- function(p) {
    if (p %in% condition.66.33.pairs) {
      '66-33'
    }
  else if (p %in% condition.83.17.pairs) {
      '83-17'
  }
  else if (p %in% condition.100.66.pairs) {
      '100-66'
  }
  else if (p %in% condition.100.33.pairs) {
      '100-33'
  }
}

#utility function to look up pair and label condition
pair.to.experiment <- function(p) {
  if ((p %in% condition.66.33.pairs) | (p %in% condition.83.17.pairs)) {
      'Experiment1'}
  else {
    'Experiment2'
  }}
 

# Reads in a pair and adds condition info and trial number
read.pair <- function(pair.id) {
  this.pair.data <- read.csv(paste(sep="",data.directory,pair.id,".txt"),stringsAsFactors=FALSE)
  this.pair.data$Pair <- pair.id
  this.pair.data$Condition <- pair.to.condition(pair.id)
  this.pair.data$Experiment <- pair.to.experiment(pair.id)
  #order Block levels to avoid them being messed up by ddply, then add trial numbers by block using ddply
  this.pair.data$Block <- factor(this.pair.data$Block,
                                    levels=c("VocabTraining",
                                             "VocabTesting",
                                             "Training",
                                             "IsolateTesting1",
                                             "InteractiveTesting",
                                             "InteractiveTesting1",
                                             "InteractiveTesting2",
                                             "IsolateTesting2"))
  this.pair.data <- ddply(this.pair.data,~ Block,transform,TrialN=1:length(Block))
  this.pair.data
}

all.data <- do.call("rbind", lapply(all.pairs, function(pair) read.pair(pair)))

#keep only blocks we need
all.data <- subset(all.data,Block %in% c("Training","IsolateTesting1","InteractiveTesting","IsolateTesting2"))

#utility function to split interaction data into two blocks for analysis
all.data$Block <- mapply(function(block,trialn)
  ifelse(block=="InteractiveTesting" & trialn<=48,"InteractiveTesting1",
         ifelse(block=="InteractiveTesting" & trialn>48,"InteractiveTesting2",
                                levels(all.data$Block)[block])),
  all.data$Block,all.data$TrialN)

#relabel blocks
all.data$Block <- revalue(all.data$Block,
                         c("Training"="Training",
                           "IsolateTesting1"="Recall 1",
                           "InteractiveTesting1"="Interaction Block 1",
                           "InteractiveTesting2"="Interaction Block 2",
                           "IsolateTesting2"="Recall 2"
              ))

```

# Organise training and recall data so that there is one line per trial

For training and recall data data from each participant is included per line, we want to split that. 

Additionally, for training data we want to keep the *target* description, not what they typed during the trivial retyping test.

```{r}
#Deal with training data
unformatted.training.data <- subset(all.data,Block=='Training')

dom.training.data <- dplyr::select(unformatted.training.data,Experiment,Condition,Pair,Block,TrialN,DomTargetAnimal,DomTargetNumber,DomTargetMotion,DomTargetDescription)
dom.training.data$Participant <- "P1"
dom.training.data <- rename(dom.training.data,
                      c('DomTargetAnimal'='Animal',
                        'DomTargetNumber'='Number',
                        'DomTargetMotion'='Movement',
                        'DomTargetDescription'='Description'))

sub.training.data <- dplyr::select(unformatted.training.data,Experiment,Condition,Pair,Block,TrialN,SubTargetAnimal,SubTargetNumber,SubTargetMotion,SubTargetDescription)
sub.training.data$Participant <- "P2"
sub.training.data <- rename(sub.training.data,
                      c('SubTargetAnimal'='Animal',
                        'SubTargetNumber'='Number',
                        'SubTargetMotion'='Movement',
                        'SubTargetDescription'='Description'))

training.data <- rbind(dom.training.data,sub.training.data)
training.data$ParticipantID <- paste(training.data$Pair,training.data$Participant,sep='')
training.data$Score <- NA #for compatability with interaction data

```

```{r}
#Deal with recall data - note that now we want their typed descriptions
unformatted.recall.data <- subset(all.data,grepl('Recall',Block))

dom.recall.data <- dplyr::select(unformatted.recall.data,Experiment,Condition,Pair,Block,TrialN,DomTargetAnimal,DomTargetNumber,DomTargetMotion,DomTypedDescription)
dom.recall.data$Participant <- "P1"
dom.recall.data <- rename(dom.recall.data,
                           c('DomTargetAnimal'='Animal',
                        'DomTargetNumber'='Number',
                        'DomTargetMotion'='Movement',
                        'DomTypedDescription'='Description'))

sub.recall.data <- dplyr::select(unformatted.recall.data,Experiment,Condition,Pair,Block,TrialN,SubTargetAnimal,SubTargetNumber,SubTargetMotion,SubTypedDescription)
sub.recall.data$Participant <- "P2"
sub.recall.data <- rename(sub.recall.data,
                           c('SubTargetAnimal'='Animal',
                        'SubTargetNumber'='Number',
                        'SubTargetMotion'='Movement',
                        'SubTypedDescription'='Description'))

recall.data <- rbind(dom.recall.data,sub.recall.data)
recall.data$ParticipantID <- paste(recall.data$Pair,recall.data$Participant,sep='')
recall.data$Score <- NA #for compatability with interaction data
```

Convert interaction data to same format. Format here in the raw data is a little different - one line per trial, direcor's text is always in the Dom column, but Director column indicates who was directing (0 = Dominant = P1)

```{r}
unformatted.interaction.data <- subset(all.data,grepl('Interaction',Block))

interaction.data <- dplyr::select(unformatted.interaction.data,Experiment,Condition,Pair,Block,TrialN,DomTargetAnimal,DomTargetNumber,DomTargetMotion,DomTypedDescription,Score,Director)
interaction.data$Participant <- ifelse(interaction.data$Director==0,'P1','P2')
interaction.data <- dplyr::select(interaction.data,-Director)
interaction.data <- rename(interaction.data,
                           c('DomTargetAnimal'='Animal',
                        'DomTargetNumber'='Number',
                        'DomTargetMotion'='Movement',
                        'DomTypedDescription'='Description'))

interaction.data$ParticipantID <- paste(interaction.data$Pair,interaction.data$Participant,sep='')
```

#Rebuild single dataframe and save

```{r}
processed.data <- rbind(training.data,recall.data,interaction.data)
processed.data$Block <- factor(processed.data$Block,
                               levels=c("Training",
                                        "Recall 1",
                                        "Interaction Block 1",
                                        "Interaction Block 2",
                                        "Recall 2"))

#sort by block etc appropriately
processed.data <- dplyr::arrange(processed.data,
                                 Experiment,Condition,Pair,Block,TrialN,Participant)

#calculate word order
processed.data$WordOrder <- mapply(function(s) identify.word.order(s),
                                   processed.data$Description)
processed.data$Marked <- mapply(function(o) is.number.marked(o),
                                   processed.data$WordOrder)
```

```{r}
write.csv(subset(processed.data,Experiment=='Experiment1'),"ProcessedData/Experiment1Data.csv")
write.csv(subset(processed.data,Experiment=='Experiment2'),"ProcessedData/Experiment2Data.csv")

```
