---
title: "Asymmetric alignment paper, analysis and graphs on combined data"
author: "Kenny Smith"
date: "2nd May 2019"
output: html_document
---

There are a small number of focussed questions where we want to look at data from both experiments. The point here is just to reiterate that individuals paired with categorical participants change more than categorical participants.

For all the analyses that follow, the question is: Do variable participants paired with categorical participants change differently from variable paired with variable? 

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

library(ggplot2)

my.colours <- c("#EA7D00","#006DE9","#808080")

set.seed(67601)

```

# Read in data and report Ns

```{r}
exp1.data <- read.csv("ProcessedData/Experiment1Data.csv")
exp2.data <- read.csv("ProcessedData/Experiment2Data.csv")

combined.data <- rbind(exp1.data,exp2.data)

plyr::ddply(combined.data,~Condition,plyr::summarise,Current_N=length(unique(Pair)))
```


# Data processing  

Need to calculate block-to-block change.

```{r}
combined.data.singulars <- subset(combined.data,Number==1)
combined.data.by.block <- aggregate(data=combined.data.singulars,
                                       Marked~Condition + Pair + Block + Participant + ParticipantID,
                                       FUN=mean)

combined.data.by.block <- plyr::rename(combined.data.by.block,c("Marked"="ProportionMarkedSingulars"))


#The most convenient way to calculate differences from block to block is to restructure the data to wide format.
combined.change.data <- tidyr::spread(data=combined.data.by.block,Block,ProportionMarkedSingulars)

combined.change.data$ChangeTrainingRecall1 <- combined.change.data$'Recall 1' - combined.change.data$'Training'

combined.change.data$ChangeRecall1Interaction2 <- combined.change.data$'Interaction Block 2'-combined.change.data$'Recall 1'

combined.change.data$ChangeRecall1Recall2 <- combined.change.data$'Recall 2'-combined.change.data$'Recall 1'

#utility function to label trials
classify.combination <- function(Condition,Participant){
  if ((Condition=="100-66" | Condition=="100-33") & Participant=="P1") {
    "Categorical"}
  else if ((Condition=="100-66" | Condition=="100-33") & Participant=="P2") {
    "Experiment 2:\nVariable paired\nwith Categorical"}
  else {"Experiment 1:\nVariable paired\nwith Variable"}
}

combined.change.data$CombinationCondition <- mapply(classify.combination,combined.change.data$Condition,combined.change.data$Participant)
#order levels the way I want
combined.change.data$CombinationCondition <- factor(combined.change.data$CombinationCondition,
                                               levels=c("Categorical",
                                                        "Experiment 1:\nVariable paired\nwith Variable",
                                                        "Experiment 2:\nVariable paired\nwith Categorical"))

```

# Looking at all data

Plot.

```{r}
ggplot(data=subset(combined.change.data,CombinationCondition!="Categorical"), aes(x=CombinationCondition, y=ChangeRecall1Interaction2, fill=CombinationCondition,ymin=-1)) +
  theme_bw() + 
  geom_boxplot() +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_y_continuous(limits=c(-1,1.1),breaks=seq(-1,1,1/3),labels=c("-1","-2/3","-1/3","0","+1/3","+2/3","+1")) +
  ylab("Change, Recall 1 to Interaction Block 2") + 
  theme(axis.title.x = element_blank()) +
  #theme(strip.text.y = element_blank()) + 
  theme(legend.position="none") 
```

```{r include=FALSE}
#Annotated plot for paper
ggplot(data=subset(combined.change.data,CombinationCondition!="Categorical"), aes(x=CombinationCondition, y=ChangeRecall1Interaction2, fill=CombinationCondition,ymin=-1)) +
  theme_bw() + 
  geom_boxplot() +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_y_continuous(limits=c(-1,1.1),breaks=seq(-1,1,1/3),labels=c("-1","-2/3","-1/3","0","+1/3","+2/3","+1")) +
  ylab("Change, Recall 1 to Interaction Block 2") + 
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y  = element_text(size=13)) +
  theme(axis.text.y  = element_text(size=11)) +
  theme(axis.text.x  = element_text(size=11)) +
  theme(legend.position="none") + 
  annotate("text",x=1.5,y=1.09,label="***",size=4) + #add p to indicate significant diff
  geom_segment(aes(x=1, y=1.09, xend=1.4, yend=1.09)) + geom_segment(aes(x=1.6, y=1.09, xend=2, yend=1.09)) + #add lines either side of text 
  ggsave(file="Plots/BothExpsChangeRecall1ToInteraction2.pdf",width=4, height=4)
```

Statistic: **Yes**, they differ.

```{r}
wilcox.test(subset(combined.change.data,CombinationCondition=="Experiment 2:\nVariable paired\nwith Categorical")$ChangeRecall1Interaction2,
            subset(combined.change.data,CombinationCondition=="Experiment 1:\nVariable paired\nwith Variable")$ChangeRecall1Interaction2)
```


# Looking only at P2s

Running the analysis on P2s only provides a tighter comparison since they are all paired with a more frequent user. **Difference is still significant**.

```{r}
ggplot(data=subset(combined.change.data,CombinationCondition!="Categorical" & Participant=="P2"), aes(x=CombinationCondition, y=ChangeRecall1Interaction2, fill=CombinationCondition),ymin=-1) +
  theme_bw() + 
  geom_boxplot() +
  #facet_grid(StageToStage~Condition,drop = TRUE) +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_x_discrete(labels=c("Experiment 1:\nVariable P2 paired\nwith Variable P1",
                            "Experiment 2:\nVariable P2 paired\nwith Categorical P1")) +
  scale_y_continuous(limits=c(-1,1.1),breaks=seq(-1,1,1/3),labels=c("-1","-2/3","-1/3","0","+1/3","+2/3","+1")) +
  ylab("Change, Recall 1 to Interaction Block 2") + 
  theme(axis.title.x = element_blank()) +
  #theme(strip.text.y = element_blank()) + 
  theme(legend.position="none") + 
  expand_limits(y=-1)
```

```{r include=FALSE}
#Plot for paper - no y axis text, annotation for significance
ggplot(data=subset(combined.change.data,CombinationCondition!="Categorical" & Participant=="P2"), aes(x=CombinationCondition, y=ChangeRecall1Interaction2, fill=CombinationCondition),ymin=-1) +
  theme_bw() + 
  geom_boxplot() +
  #facet_grid(StageToStage~Condition,drop = TRUE) +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_x_discrete(labels=c("Experiment 1:\nVariable P2 paired\nwith Variable P1",
                            "Experiment 2:\nVariable P2 paired\nwith Categorical P1")) +
  expand_limits(y=-1) +
  theme(legend.position="none") + 
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_blank()) +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()) +
  theme(axis.text.x  = element_text(size=11)) +
  annotate("text",x=1.5,y=1.09,label="**",size=4) + #add p to indicate significant diff
  geom_segment(aes(x=1, y=1.09, xend=1.4, yend=1.09)) + geom_segment(aes(x=1.6, y=1.09, xend=2, yend=1.09)) + #add lines either side of text 
  ggsave(file="Plots/BothExpsChangeRecall1ToInteraction2P2sOnly.pdf",width=4, height=4)
```

```{r}
wilcox.test(subset(combined.change.data,CombinationCondition=="Experiment 2:\nVariable paired\nwith Categorical" & Participant=="P2")$ChangeRecall1Interaction2,
            subset(combined.change.data,CombinationCondition=="Experiment 1:\nVariable paired\nwith Variable"& Participant=="P2")$ChangeRecall1Interaction2)
```

# Looking only at 33% trained participants

Since we have 33%-trained participants in both experiments we can compare these. Answer is **yes**, they still differ based on whether their partner was categorical or variable. 
```{r}
ggplot(data=subset(combined.change.data,(Condition=="100-33" & Participant=="P2") | (Condition=="66-33" & Participant=="P2")), aes(x=CombinationCondition, y=ChangeRecall1Interaction2, fill=CombinationCondition)) +
  theme_bw() + 
  geom_boxplot() +
  #facet_grid(StageToStage~Condition,drop = TRUE) +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_x_discrete(labels=c("Trained on 33%,\npaired with\nVariable P1",
                            "Trained on 33%,\npaired with\nCategorical P1")) +
  scale_y_continuous(limits=c(-1,1.1),breaks=seq(-1,1,1/3),labels=c("-1","-2/3","-1/3","0","+1/3","+2/3","+1")) +
  ylab("Change, Recall 1 to Interaction Block 2") + 
  theme(axis.title.x = element_blank()) +
  #theme(strip.text.y = element_blank()) + 
  theme(legend.position="none") 
```

```{r include=FALSE}
#Plot for paper
ggplot(data=subset(combined.change.data,(Condition=="100-33" & Participant=="P2") | (Condition=="66-33" & Participant=="P2")), aes(x=CombinationCondition, y=ChangeRecall1Interaction2, fill=CombinationCondition)) +
  theme_bw() + 
  geom_boxplot() +
  #facet_grid(StageToStage~Condition,drop = TRUE) +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_x_discrete(labels=c("Trained on 33%,\npaired with\nVariable P1",
                            "Trained on 33%,\npaired with\nCategorical P1")) +
  scale_y_continuous(limits=c(-1,1.1),breaks=seq(-1,1,1/3),labels=c("-1","-2/3","-1/3","0","+1/3","+2/3","+1")) +
  ylab("Change, Recall 1 to Interaction Block 2") + 
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y  = element_text(size=13)) +
  theme(axis.text.y  = element_text(size=11)) +
  theme(axis.text.x  = element_text(size=11)) +
  theme(legend.position="none") + 
  annotate("text",x=1.5,y=1.09,label="**",size=4) + #add * to indicate significant diff
  geom_segment(aes(x=1, y=1.09, xend=1.4, yend=1.09)) + geom_segment(aes(x=1.6, y=1.09, xend=2, yend=1.09)) + #add lines either side of text 
  
  ggsave(file="Plots/BothExpsChangeRecall1ToInteraction233sOnly.pdf",width=4, height=4)
```

```{r}
wilcox.test(subset(combined.change.data,(Condition=="100-33" & Participant=="P2"))$ChangeRecall1Interaction2,
            subset(combined.change.data,(Condition=="66-33" & Participant=="P2"))$ChangeRecall1Interaction2)
```

# Analysis looking at participants who were categorical at Recall 1

Finally, it might be that the relevant measure of categoricalness is not their training, but what a participant produced at Recall 1. Do variably-trained participants who were categorical users at Recall 1 look like categorical participants in terms of their willingness to change? Note that we are including only categorical users in this analysis. 

```{r}
combined.change.data$CategoricalAtTraining <- combined.change.data$Training==1
#This would be on the categorical users + non-users, but I think the latter are not quite comparable
#combined.change.data$CategoricalAtRecall1 <- (combined.change.data$'Recall 1'==1 | combined.change.data$'Recall 1'==0)
combined.change.data$CategoricalAtRecall1 <- (combined.change.data$'Recall 1'==1)

#useful for qualitative observations
combined.change.data$CategoricalUserAtInteraction2 <- (combined.change.data$'Interaction Block 2'==1)
combined.change.data$CategoricalNonUserAtInteraction2 <- (combined.change.data$'Interaction Block 2'==0)
combined.change.data$NotCategoricalUserAtInteraction2 <- (combined.change.data$'Interaction Block 2'<1)

plyr::ddply(combined.change.data,~Condition+CategoricalAtTraining+CategoricalAtRecall1,plyr::summarise,Current_N=length(unique(ParticipantID)))

combined.change.data.categorical.recall1 <- subset(combined.change.data,CategoricalAtRecall1)

plyr::ddply(combined.change.data.categorical.recall1,~CategoricalAtTraining+CategoricalAtRecall1,plyr::summarise,Current_N=length(unique(ParticipantID)))

#in the text we report what the variably-trained-but-categorical people did during interaction
#the subsetting is to restrict us to vartiably-trained participants
plyr::ddply(subset(combined.change.data,!CategoricalAtTraining & CategoricalAtRecall1), ~CategoricalUserAtInteraction2+CategoricalNonUserAtInteraction2+NotCategoricalUserAtInteraction2,plyr::summarise,Current_N=length(unique(ParticipantID)))

#and here is the equivalent for categorically-trained participants
plyr::ddply(subset(combined.change.data,CategoricalAtTraining), ~CategoricalUserAtInteraction2+CategoricalNonUserAtInteraction2+NotCategoricalUserAtInteraction2,plyr::summarise,Current_N=length(unique(ParticipantID)))


```

Do the categorically-trained participants differ form the ones who happen to be categorical in Recall 1? **No**, they don't.

```{r}
ggplot(data=combined.change.data.categorical.recall1, aes(x=CategoricalAtTraining, y=ChangeRecall1Interaction2, fill=CategoricalAtTraining)) +
  theme_bw() + 
  geom_boxplot() +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_x_discrete(labels=c("Variable training,\ncategorical user at Recall 1\n(N=22)",
                            "Categorical training,\ncategorical user at Recall 1\n(N=40)")) +
  scale_y_continuous(limits=c(-1,1.1),breaks=seq(-1,1,1/3),labels=c("-1","-2/3","-1/3","0","+1/3","+2/3","+1")) +
  ylab("Change, Recall 1 to Interaction Block 2") + 
  theme(axis.title.x = element_blank()) +
  theme(legend.position="none") 
```

```{r include=FALSE}
#plot for paper - no y axis text, annotation
ggplot(data=combined.change.data.categorical.recall1, aes(x=CategoricalAtTraining, y=ChangeRecall1Interaction2, fill=CategoricalAtTraining)) +
  theme_bw() + 
  geom_boxplot() +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_x_discrete(labels=c("Variable training,\ncategorical user\nat Recall 1 (N=22)",
                            "Categorical training,\ncategorical user\nat Recall 1 (N=40)")) +
  scale_y_continuous(limits=c(-1,1.1),breaks=seq(-1,1,1/3),labels=c("-1","-2/3","-1/3","0","+1/3","+2/3","+1")) +
  ylab("Change, Recall 1 to Interaction Block 2") + 
  theme(axis.title.x = element_blank()) +
  theme(legend.position="none") + 
  theme(axis.title.y = element_blank()) +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()) +
  theme(axis.text.x  = element_text(size=11)) +
  annotate("text",x=1.5,y=1.09,label="n.s.",size=4) + #add p to indicate significant diff
  geom_segment(aes(x=1, y=1.09, xend=1.4, yend=1.09)) + geom_segment(aes(x=1.6, y=1.09, xend=2, yend=1.09)) + #add lines either side of text 
  ggsave(file="Plots/BothExpsChangeRecall1ToInteraction2CategoricalAtRecall1.pdf",width=4, height=4)
```

```{r}
wilcox.test(subset(combined.change.data.categorical.recall1,CategoricalAtTraining)$ChangeRecall1Interaction2,
            subset(combined.change.data.categorical.recall1,!CategoricalAtTraining)$ChangeRecall1Interaction2)
```


Can do same thing on the change from recall 1 to recall 2, but is it informative?

```{r}
ggplot(data=combined.change.data.categorical.recall1, aes(x=CategoricalAtTraining, y=ChangeRecall1Recall2, fill=CategoricalAtTraining)) +
  theme_bw() + 
  geom_boxplot() +
  #facet_grid(StageToStage~Condition,drop = TRUE) +
  scale_fill_manual(values=c(my.colours[2],my.colours[1])) +
  scale_x_discrete(labels=c("Variable training,\ncategorical user at Recall 1\n(N=22)",
                            "Categorical training,\ncategorical user at Recall 1\n(N=40)")) +
  scale_y_continuous(breaks=seq(-1,1,1/3),labels=c("-1","-2/3","-1/3","0","+1/3","+2/3","+1")) +
  ylab("Change, Recall 1 to Recall 2") + 
  theme(axis.title.x = element_blank()) +
  #theme(strip.text.y = element_blank()) + 
  theme(legend.position="none") + 
  expand_limits(y=-1) 

```

```{r}
wilcox.test(subset(combined.change.data.categorical.recall1,CategoricalAtTraining)$ChangeRecall1Recall2,
            subset(combined.change.data.categorical.recall1,!CategoricalAtTraining)$ChangeRecall1Recall2)
```

  
  
  
  